LFQ: Online Learning of Per-flow Queuing Policies using Deep Reinforcement Learning

### 2020-07-14 paper/paper.tex
Add documentation for parameters in rl.cc

\newacronym{dl}{DL}{Deep Learning}
\newacronym{rl}{RL}{Reinforcement Learning}
\newacronym{ours}{LFQ}{Fair Learning Qdisc}
\newacronym{cca}{CCA}{Congestion Control Algorithm}
\newacronym{aqm}{AQM}{Active Queue Management}
\newacronym{rtt}{RTT}{Round Trip Time}
\newacronym{fq}{FQ}{Fair Queuing}
\newacronym{ml}{ML}{Machine Learning}
\newacronym{bdp}{BDP}{Bandwidth Delay Product}
\newacronym{mae}{MAE}{Mean Absolute Error}
\newacronym{mse}{MSE}{Mean Squared Error}
\newacronym{qoe}{QoE}{Quality of Experience}

@@

\begin{abstract}
The increasing number of different, incompatible congestion control algorithms has led to an increased deployment of fair queuing. Fair queuing isolates each network flow and can thus guarantee fairness for each flow even if the flows' congestion controls are not inherently fair. So far, each queue in the fair queuing system either has a fixed, static maximum size or is managed by an Active Queue Management (AQM) algorithm like CoDel. In this paper we design an AQM mechanism (Fair Learning Qdisc (LFQ)) that dynamically learns the optimal buffer size for each flow according to a specified reward function online. We show that our Deep Learning based algorithm can dynamically assign the optimal queue size to each flow depending on its congestion control, delay and bandwidth. Comparing to competing fair AQM schedulers, it provides significantly smaller queues while achieving the same or higher throughput. 
\end{abstract}

@@

New \glspl{cca} for TCP and QUIC are still being introduced, revisiting old ideas but also introducing new concepts \cite{dong_pcc_2018, cardwell_bbr:_2016, hock_tcp_2017, bachl_cocoa_2019, jay_deep_2019}. Some of them, such as BBR, are already being used in real-world production systems. While new \glspl{cca} are commonly being designed with compatibility to other \glspl{cca} in mind, often they do not share the link completely fairly with older \glspl{cca} \cite{hock_experimental_2017, fejes_who_2019, fejes_incompatibility_2020}. Besides that, network flows using the same \gls{cca} can also be unfair to each other: For example, BBR favors flows with a high \gls{rtt}, while New Reno favors those with a low one \cite{turkovic_interactions_2019,turkovic_fifty_2019}. This unfairness can be mitigated by using \gls{fq} at the bottleneck link, isolating each flow from all other flows and assigning each flow an equal share of bandwidth \cite{dumazet_pkt_sched:_2013}.

@@

>>>>

\newacronym{dl}{DL}{Deep Learning}
\newacronym{rl}{RL}{Reinforcement Learning}
\newacronym{ours}{LFQ}{Learning Fair Qdisc}
\newacronym{cca}{CCA}{Congestion Control Algorithm}
\newacronym{aqm}{AQM}{Active Queue Management}
\newacronym{rtt}{RTT}{Round Trip Time}
\newacronym{fq}{FQ}{Fair Queuing}
\newacronym{ml}{ML}{Machine Learning}
\newacronym{bdp}{BDP}{Bandwidth Delay Product}
\newacronym{mae}{MAE}{Mean Absolute Error}
\newacronym{mse}{MSE}{Mean Squared Error}
\newacronym{qoe}{QoE}{Quality of Experience}

@@

\begin{abstract}
The increasing number of different, incompatible congestion control algorithms has led to an increased deployment of fair queuing. Fair queuing isolates each network flow and can thus guarantee fairness for each flow even if the flows' congestion controls are not inherently fair. So far, each queue in the fair queuing system either has a fixed, static maximum size or is managed by an Active Queue Management (AQM) algorithm like CoDel. In this paper we design an AQM mechanism (Learning Fair Qdisc (LFQ)) that dynamically learns the optimal buffer size for each flow according to a specified reward function online. We show that our Deep Learning based algorithm can dynamically assign the optimal queue size to each flow depending on its congestion control, delay and bandwidth. Comparing to competing fair AQM schedulers, it provides significantly smaller queues while achieving the same or higher throughput. 
\end{abstract}

@@

New \glspl{cca} for TCP and QUIC are still being introduced, revisiting old ideas but also introducing new concepts \cite{dong_pcc_2018, cardwell_bbr:_2016, hock_tcp_2017, bachl_rax_2019, jay_deep_2019}. Some of them, such as BBR, are already being used in real-world production systems. While new \glspl{cca} are commonly being designed with compatibility to other \glspl{cca} in mind, often they do not share the link completely fairly with older \glspl{cca} \cite{hock_experimental_2017, fejes_who_2019, fejes_incompatibility_2020}. Besides that, network flows using the same \gls{cca} can also be unfair to each other: For example, BBR favors flows with a high \gls{rtt}, while New Reno favors those with a low one \cite{turkovic_interactions_2019,turkovic_fifty_2019}. This unfairness can be mitigated by using \gls{fq} at the bottleneck link, isolating each flow from all other flows and assigning each flow an equal share of bandwidth \cite{dumazet_pkt_sched:_2013}.

@@

Besides \gls{aqm}, Deep \gls{rl} has proven to be successful in several other domains of networking such as Congestion Control \cite{jay_deep_2019,bachl_rax_2019}, Traffic Engineering \cite{xu_experience-driven_2018} and Intelligent Packet Sampling for saving computational resources \cite{bachl_sparseids_2020}.
